Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-02-22 Ben_Manuscripts/transport/Outline.tex
Outline updoots

  In this work, we have determined the transport mechanisms and macroscopic
  transport properties exhibited by a number of polar solutes with varying size,
  chemical functionality and hydrophilic character.
  \begin{itemize}
	\item Many of the separations we are interested in involve polar organic 
	compounds.
  \end{itemize}

  We have compared our calculated diffusion coefficients with experimental
  measurements made using DOSY NMR.

@@

@@

  \subsection*{Transport of Ketones}

>>>>

  In this work, we have studied the transport mechanisms exhibited by a number
  of polar solutes with varying size, chemical functionality and hydrophilic character.
  \begin{itemize}
	\item Many of the separations we are interested in involve polar organic 
	compounds.
  \end{itemize}

  There are a number of questions that we wish to answer in order to create a
  framework for studying this system in even greater detail.
  \begin{enumerate}

   	\item What transport mechanisms do we observe?

  	Given that the pores will restrict motion of the solutes, we anticipate that 
  	transport will be hindered in some way. We want to understand the differences in
  	solute motion, specifically its mean squared displacement (MSD), based on a solute's
  	size and chemical identity (functional groups). We will study the interactions
  	between solutes, the membrane, and water in order to determine which mechanism
  	or mechanisms dominate.

%  	are dictated by a 
%  	solute's chemical identity and if so, what interactions lead to this
%  	difference.

  	\item How do molecules, including water, partition within the pores?

  	From a macroscopic perspective, it is straightforward to hypothesize that the water and
  	polar solutes spend their time exclusively in the tube-like hydrophilic pore region.
  	Our previous work showed that there is a gradual compositional transition from the 
  	hydrophilic to the hydrophobic region which means that solutes may not 
  	necessarily stay confined to the centers of the pores or even within the
  	pore region. We will study the gradient in composition of solutes and water
  	and any resultant influence it might have on mechanistic properties.

  	\item Can we describe the transport mechanisms using pre-existing 
  	mathematical models.

  	A mathematical model may provide additional insight into the transport
  	mechanisms and, in future work, can help relate performance on the 
  	timescales studied with MD to macroscopic timescales. We will use
  	qualitative and semi-quantitative arguments in order to choose a 
  	governing model.

  	\item How can we modify the current monomers in order to enhance
  	solute-specific separations?

  	Most experimental characterization up to this point has been centered 
  	around the monomer, Na-GA3C11, studied here. The primary reason for conducting
  	these simulations is to understand what chemical modifications can be made 
  	to this or similar liquid crystal molecules in order to enhance transport 
  	of desired species or restrict that of undesired species. We will use the 
  	insight gained from our mechanistic observations in order to suggest new 
  	monomer designs.

  \end{enumerate}

  There are number of questions this study is not intended to answer.
  \begin{itemize}
    \item We will not study the concentration dependence of the observed
    transport rates. Although the average MSD might change with concentration,
    we are focused on the underlying interactions leading to the observed 
    transport mechanisms which we conjecture will be the same regardless of
    concentration.
    \item We will not study the chemical potential of solutes in the pores, which
    could give us a better understanding of equilibrium solute partitioning.
    However, this information will not greatly enhance our understanding of 
    mechanistic details in various membrane regions.
    \item Both of the above points will add unnecessary levels of complexity
    which can be left for a future study. 
%    \item Our work is meant as a simple starting point for studying transport
%    mechanisms in these complex LLC systems.
    \item This work is a simple starting point meant for observing the types
    of interactions which occur between isolated solutes and the membrane.
  \end{itemize}

@@

  We will answer the questions posed in the introduction in a general 
  sense before addressing them with respect to specific molecules.

@@

  \subsection*{Transport of Ketones and Amides}
